Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
Packrat, param

 ```{r adonis calculation}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = var.CL.min,
                                           npermutations = 10000)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = var.CL,
                                           npermutations = 10000)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

@@

    maaslin <- Maaslin2(maaslin.abund,
             maaslin.pheno,
             paste0("cache/maaslin-", now),
             transform = 'AST',
             fixed_effects = paste0(var.CL, collapse = ","), 
             cores = detectCores())

>>>>

 ```{r adonis calculation, eval = FALSE}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = var.CL.min,
                                           npermutations = 10000)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = var.CL,
                                           npermutations = 10000)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

@@

    maaslin <- Maaslin2(maaslin.abund,
             maaslin.pheno,
             paste0("cache/maaslin-", now),
             transform = 'AST',
		normalization = "NONE",
		random_effects = paste0(var.BP, collapse = ","),
             fixed_effects = paste0(var.CL, collapse = ","), 
             cores = detectCores())
